Analysis and Figures for Gallego et al, 2020

### 2020-09-04 Scripts/Manuscript.Main.Analysis.Rmd
Wilcox

input.richness %>% 
  nest(-Area) %>% 
  mutate(data = map (data, ~ .x %>% 
                         group_by(Year,  sim.row) %>% 
                         summarise( Richness = sum(present)) ),
         lm = map(data, ~ lm(Richness ~ Year, data = .x)),
         tidy_lm = map(lm, broom::tidy)) %>%
  unnest(tidy_lm)

input.richness %>% 
  nest(-phylum,) %>% 
  #  slice(1) %>%
    mutate(data = map (data, ~ .x %>% 
                         group_by(Year,  sim.row) %>% 
                         summarise( Richness = sum(present)) )) %>% 
   mutate(wilcoxon = map (data, ~ wilcox.test(Richness ~ Year, data = .x) ))  -> results.lm

>>>>

input.richness %>% 
  nest(-Area) %>% 
  mutate(data = map (data, ~ .x %>% 
                       mutate(present = case_when(present < 0.5 ~ 0,
                                                  TRUE          ~ 1)) %>% 
                         group_by(Year,  sim.row) %>% 
                         summarise( Richness = sum(present)) ),
         wilcoxon = map(data, ~ wilcox.test(Richness ~ Year, data = .x, alternative = "greater")),
         tidy_wilcox = map(wilcoxon, broom::tidy)) %>%
  pull(wilcoxon)

## We cannot

input.richness %>% 
  nest(-phylum,-Area) %>% 
  #  slice(1) %>%
    mutate(data = map (data, ~ .x %>% 
                         mutate(present = case_when(present < 0.5 ~ 0,
                                                  TRUE          ~ 1)) %>% 
                         group_by(Year,  sim.row) %>% 
                         summarise( Richness = sum(present)) )) %>% 
   mutate(wilcoxon = map (data, ~ wilcox.test(Richness ~ Year, data = .x, alternative = "greater") ))  -> results.lm
